Creating an Arrow IPC file from the NYC 311 data

### 2023-06-17 nyc311clean.qmd
Minor edits to clean up text

We now have enough information, such as the date-time format used, to do an initial conversion of the CSV file to a `DataFrame`, using several optional arguments to customize the process.
(Details about each of these optional arguments are given callout blocks below.)

@@

Some columns are given are `String` whereas others are given as `String7` or `String15`.
These are storage-saving representations used when the whole column consists of short character strings.
There is an anomaly in these short strings for the `Agency` column.
The `Agency` acronyms should be 4 or 5 characters at most but at least one (it happens to be `NYC311-PRD`) must be greater than 7 characters to force `String15` storage.

@@

The other problem shown in the types is that the `Incident_Zip` column is stored as strings when they should be integers.

@@

or Python (note that this format is called `feather` in the `pyarrow` package)

>>>>

We now have enough information, such as the date-time format used, to do an initial conversion of the CSV file to a `DataFrame`, using several optional arguments to customize the process.
(Details about each of these optional arguments are given in callout blocks below.)

@@

Some columns are described as `String` whereas others are described as `String7` or `String15`.
These are storage-saving representations used when the whole column consists of short character strings.
There is an anomaly in these short strings for the `Agency` column.
The `Agency` acronyms should be 4 or 5 characters at most but at least one (it happens to be `NYC311-PRD`) must be greater than 7 characters to force `String15` storage.

@@

The other problem shown in the types is that the values in the `Incident_Zip` column are stored as strings when they should be integers or missing.

@@

or Python (note that the Arrow IPC format is called `feather` in the `pyarrow` package) or in [Polars](https://pola.rs)
